---
output: html_document
---
# Machine Learning Project  

Loading Data and Packages  
```{r}
library(caret)                                             
library(randomForest)
library(caTools)  
library(rpart)
library(rpart.plot)  
data = read.csv("pml-training.csv")
test = read.csv("pml-testing.csv")
```  
Splitting training data into training and testing sets  
```{r}
inTrain = createDataPartition(y=data$classe,p=0.7,list=FALSE)
training = data[inTrain,]
testing = data[-inTrain,]
```  

#split = sample.split(data$classe, SplitRatio = 0.6)
#training = subset(data, split == TRUE)
#testing = subset(data, split == FALSE)  

Removing useless variabes with no variance  
```{r}
useless <- nearZeroVar(training)
training <- training[, -useless]
```  


Training a Tree Model  
```{r}
Tree = rpart(classe ~., data=training, method="class", control=rpart.control(minbucket=100))
prp(Tree)
```  

Predicting the validation data and evaluating performance  
```{r}
PredictCART = predict(Tree, newdata=testing, type="class")
table(testing$classe, PredictCART)
print(confusionMatrix(PredictCART, testing$classe))
```  

Model has 87% accuracy on new data set with Kappa of 83%
